---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# chartbox

<!-- badges: start -->
<!-- badges: end -->

The `chartbox` package stores generated growth charts. With the package you can 

- list the available growth charts;
- set the color palette;
- load one of the growth charts for further processing.

The package obtains its charts from the 
[chartdesigner](https://github.com/stefvanbuuren/chartdesigner) package.

## Installation

In order to install `chartbox` you need a personal access token (PAT) from <https://github.com/settings/tokens>. I assume the token is stored in the environmental variable `GITHUB_PAT`, so that `Sys.getenv("GITHUB_PAT")` returns your token.

The following statements will install the `chartbox` package

```{r eval = FALSE}
install.packages("remotes")
remotes::install_github("stefvanbuuren/chartbox")
```

## Example

The `load_chart()` function makes the stored growth charts available
for further processing. Here's an example that writes chart `PJAAN25`
to a PDF file.

```{r example}
library(chartbox)

# choose and load chart
chartcode <- "PJAAN25"
g <- load_chart(chartcode)

# set the correct color palette
pop <- chartcatalog::parse_chartcode(chartcode)$population
old_pal <- palette(palettes[pop, ])

# create the pdf
pdf(paste(chartcode, "pdf", sep = "."), height = 29.7/2.54, width = 21/2.54)
grid::grid.draw(g)
dev.off()

# restore palette
palette(old_pal)
```

